---
title: "HW2_ggplot"
author: "TYTso"
date: "2019/7/16"
output: html_document
---
# Objective    
## To figure out the relationship between lung, bronchial and tracheal-related cancer incidence rate and Observation of particulate matter (PM) in the air in 2015 and gender differences

data source (cancer): https://data.gov.tw/dataset/6399   
data source (PM): https://data.gov.tw/dataset/100047 

### the relationship between lung, bronchial and tracheal-related cancer incidence rate and Observation of particulate matter (PM) in the air in 2015

## Data Processing
```{r}
path = "D:/TSO/cancer.xlsx"
path2 = "D:/TSO/pm25.xlsx"

library(tidyverse)
library(readxl)
nccancer = read_excel(path)
ncpm = read_excel(path2)

cancer=select(nccancer,"癌症診斷年","性別","縣市別","癌症別","癌症發生數","平均年齡")

cancerlung=filter(cancer,癌症診斷年%in% c("2005":"2015"),癌症別 =="肺、支氣管及氣管",縣市別=="台北市",性別=="不分男女")
pm=select(ncpm,"月份","監測站","日平均值超過125μg/m3之日數(%)")
pm104<- pm[grep("104年", pm$"月份"),]

pmto1=0
pmto2<-0
pmto3=0
pmto4<-0
pmto5=0
pmto6<-0
pmto7=0
pmto8<-0
pmto9=0
pmto10<-0
pmto11=0
pmto12<-0

for (i in 1:8){
  pmto1<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto1
}
for (i in 10:17){
  pmto2<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto2
}
for (i in 18:25){
  pmto3<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto3
}
for (i in 26:33){
  pmto4<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto4
}
for (i in 34:41){
  pmto5<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto5
}
for (i in 42:49){
  pmto6<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto6
}
for (i in 50:57){
  pmto7<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto7
}
for (i in 58:65){
  pmto8<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto8
}
for (i in 66:73){
  pmto9<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto9
}
for (i in 74:81){
  pmto10<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto10
}
for (i in 82:89){
  pmto11<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto11
}
for (i in 89:96){
  pmto12<-pm104[i,"日平均值超過125μg/m3之日數(%)"]+pmto12
}
ptof <- data.frame("年份"=c(2005:2015),"月平均值超過125μg/m3之日數(%)"=c(pmto1[1,1],pmto2[1,1],pmto3[1,1],pmto4[1,1],pmto5[1,1],pmto6[1,1],pmto7[1,1],pmto8[1,1],pmto8[1,1],pmto9[1,1],pmto10[1,1]))


```

## lung cancer is increase yearly
```{r}
ggplot(cancerlung, aes(x=癌症診斷年, y=癌症發生數)) + geom_line(color="red") + geom_point() +ylim(1000, max(cancerlung$癌症發生數)) 
```